\documentclass[10pt]{article}

\usepackage{fullpage}
\title{Tor Fingerprinting Attack: Project Plan}
\author{Nathan Dautenhahn}
\begin{document}
\maketitle

\section{Introduction}
This document will define the initial project direction and time-line.
The general overview of our approach consists of several phases. Phase 1
will be to conduct general purpose research, in which the team will learn
about the Tor architecture. Once a general understanding of the Tor 
architecture is gained the team will focus on an in depth analysis of 
the different modules that are directly related to the fingerprinting
attack. In this way we will be able to understand Tor from the overall 
perspective, and then get in depth coverage where it matters most. This
will allow us to get up to speed on Tor as quickly as possible allotting
maximum time to perform implementation of the attack. Phase 2 will 
consist of the team brainstorming several attack vectors based upon our
previous research. Once this phase is completed we will validate the 
options and start implementation. 

\section{Road Map}
Meetings will be conducted weekly to allow for quick feedback to change
the direction of the project if needed. 

\subsection{Tor Research (2 weeks)}
\begin{itemize}
	\item \textbf{(1 week)} Tor Architecture: read literature about how 
		Tor works at general architecture level. 
	\item \textbf{(1 week)} In Depth Research: read literature specific to the 
		fingerprinting attack. At this point we will define three
		focuses for further research that will be given as a task to each 
		member. In doing this we will cover more ground than if we all 
		performed the same research. 
\end{itemize}


\subsection{Brainstorming (2 weeks)}
This phase will consist of a brainstorming session in which we discuss the 
potential ways to implement our fingerprinting attack. We will come up with 
several ideas that we will then research in order to check the validity 
of each approach. 
\paragraph{}Some of the questions this phase should answer are: 
\begin{itemize}
	\item What type of signature will we use to fingerprint the websites?  
	\item Where will we attempt to perform fingerprinting?
	\item Will we analyze encrypted packets? 
	\item Any other questions???
\end{itemize}

\subsection{Implementation (4 weeks???)}
Self explanatory implementation period should extend from all prior research.

\section{Meeting Agendas}
\begin{enumerate}
	\item Meeting 9.26.09 4:30pm CSL 221
		\begin{itemize} 
			\item Identify specific areas to understand better that directly 
				correlate to the fingerprinting attack 
			\item Assign research for the next week
		\end{itemize}
	\item Meeting TBD
		\begin{itemize}
			\item Present research findings
			\item Brainstorm attack vectors based on findings
			\item Next week will consists of researching the possible
				attack vectors
		\end{itemize}
	\item Meeting TBD
		\begin{itemize}
			\item Present findings
			\item More brainstorming
			\item If prepared start testing out implementation opportunities
		\end{itemize}
\end{enumerate}
\end{document}
